\section{Experience}
\esp
\cventry{2012--2015}{Contractual Researcher}{Inria}{Montbonnot 
Saint-Martin (Grenoble Area), France}{}{
\textbf{Trace analysis based on aggregation, visualization and interaction techniques}
\begin{itemize}
 \item Design of overview methods based on data aggregation for the analysis of voluminous execution traces provided by real-time embedded systems or HPC systems.
 \item Design and implementation of an open-source analysis tool, \textbf{Ocelotl}, and a data aggregation library, \textbf{LPAggreg}. Contributor in the development of the \textbf{Framesoc} analysis infrastructure.
 \item Collaborations within the SoC-Trace project with STMicroelectronics, within the ANR project SONGS, and within the LICIA french-brazilian laboratory.
 \item 3 publications in international conferences.
 \item Supervising an engineer and an intern.
\end{itemize}
 \textbf{Keywords: trace visualization, information visualization, big data, data aggregation, embedded systems, HPC, Java, C/C++}
}
\esp
\cventry{2012--2014}{Contractual Teacher}{Polytech'Grenoble Engineering School}{Saint-Martin d'H\`eres (Grenoble Area), France}{}{
\begin{itemize}
\item Teaching programming (128 hours): client-server project (POSIX, System V), HCI project (Swing), algorithmic and object programming practicals (Java), C and C++ practicals.
\end{itemize}
}
\esp
\cventry{2011 (6 months)}{Engineering Intern}{Thales Communications and Security, S.A.}{Paris Area, France}{}{
\textbf{Performance analysis of embedded systems}
\begin{itemize}
\item Design and implementation of POSIX and DVFS/ORB benchmarks.
\item Performance evaluation of several hardware and software combinations of real-time and embedded architectures.
\end{itemize}
\textbf{Keywords: benchmarking, embedded systems, POSIX, C/C++, Linux, ARM Cortex A8/A9}
}
\esp
\cventry{2010 (2 Months)}{Research Engineer}{LIP6, Universit\'e Pierre et Marie Curie Paris VI}{Paris, France}{}{
\textbf{Design space exploration of a virtually prototyped telecommunication application}\\
\textbf{Keywords: DSX, SocLib, MPSoC, task farm, SystemC, Python}
}
